Reviewer comments from PeerJ

### 2015-02-20 PeerJResponse.tex
Edits for reviewer 1
Edits to response and track changes text
Edits reviewer 1
Edits to response

\lev{Okay reword.}

16) Lines 249-250. 'average r2 is slightly lower in the tb1 region..' Also, include these mean values as a row in Table 3. \\

\lev{Do you guys want to do this?}

\mbh{simple enough to make the reviewer happy here and just add one more row to the table}

>>>>

\res{Thank you for the suggestion. We have reworded this sentence, page 9, lines 221-221: ``in all populations except La Mesa, where a slightly negative value suggests a slight excess of low frequency variants."}

16) Lines 249-250. 'average r2 is slightly lower in the tb1 region..' Also, include these mean values as a row in Table 3.\\

\res{The numbers reflected in Table 3 are averages.}
